Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-10-31 paper/paper.qmd
Typo updated.

## Calculate Mean Squared Error and Mean Absolute Error on Test Data
```{r}
#| echo: false
#| label: fig-diagnosis-2
#| tbl-cap: Calculate Mean Squared Error (MSE) on test data
#| warning: false
#| message: false

@@

# Display the metrics table using kable
kable(metrics_df, caption = "Model Performance Metrics on Test Data")
```

@@

# Display the full summary table using kable
kable(full_summary_df, caption = "Regression Model Summary with Additional Statistics")
```

## Multicollinearity Check on the Training Data
```{r}
#| echo: false
#| warning: false
#| message: false

@@

# Print the correlation matrix
print(cor_matrix)

# Create a beautiful correlation plot with modified labels
corrplot(
  cor_matrix, 
  method = "color",      # Use color to fill the matrix
  type = "upper",        # Show only the upper triangle
  addCoef.col = "black", # Add correlation coefficients in black
  tl.col = "black",      # Label text color
  tl.srt = 45,           # Rotate labels
  number.cex = 0.8,      # Text size for coefficients
  col = colorRampPalette(c("red", "white", "blue"))(200) # Color gradient
)

>>>>

## Calculate Mean Squared Error and Mean Absolute Error on Test Data
```{r}
#| echo: false
#| label: fig-diagnosis-2
#| tbl-cap: Calculate Mean Squared Error (MSE) on Test Data
#| warning: false
#| message: false

@@

# Display the metrics table using kable
kable(metrics_df)
```

@@

# Display the full summary table using kable
kable(full_summary_df)
```

## Multicollinearity Check on the Training Data
```{r}
#| echo: false
#| fig-cap: Correlation Matrix of "Numeric Grade", "Sample Size", "Transparency Score"and "Days Until Election"
#| warning: false
#| message: false

@@

# Create a beautiful correlation plot with modified labels
corrplot(
  cor_matrix, 
  method = "color",      
  type = "upper",        
  addCoef.col = "black", 
  tl.col = "black",      
  tl.srt = 45,          
  number.cex = 0.8,      
  col = colorRampPalette(c("red", "white", "blue"))(200) )
